Effects

### 2019-12-30 doc/Effects.Rmd
working on effect docs

@@

```{r MLH1.histogram.2, echo=FALSE}
#remake the pooled MLH1 histgoram plot from above but facet by quality

@@

```{r age.effect.model, include=FALSE}
#run a age effect linear regression!

male.data <- AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$sex.y == "male",]

male.data.dom <- male.data[male.data$subsp.y == "Dom",]

male.data.musc.low <- male.data[(male.data$strain.x == "KAZ" | male.data$strain.x == "TOM" | male.data$strain.x == "AST"),]

male.data.musc.high <- male.data[(male.data$strain.x == "PWD" | male.data$strain.x == "MSM" | male.data$strain.x == "MOLF" | male.data$strain.x == "SKIVE"),]

male.data.outgroup <- male.data[(male.data$subsp.y == "Spretus" | male.data$subsp.y == "Spic" | male.data$subsp.y == "Caroli"),]

@@

summary(lm.me.OG)
#for all models, mostly it was that the intercept was significant, and mot much else

#good knitting output
#as.data.frame( round(  summary(HetC.MixedModel.HQ)$tTable, 6 ) )

@@

AP_mouse_table_w.Ages <- add_category(AP_mouse_table_w.Ages)
#remove NAs
AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[!(is.na(AP_mouse_table_w.Ages$Nmice) | AP_mouse_table_w.Ages$Nmice==""), ]

@@

>>>>

```{r setupdata, echo=FALSE}
AP_mouse_table_w.Ages <- add_category(AP_mouse_table_w.Ages)
#remove NAs
AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[!(is.na(AP_mouse_table_w.Ages$Nmice) | AP_mouse_table_w.Ages$Nmice==""), ]

@@

```{r MLH1.histogram.2, echo=FALSE, include=FALSE}
#remake the pooled MLH1 histgoram plot from above but facet by quality

@@

I made 3 models for 3 groupings of mice, dom, musc.high and musc.low

$$mouse .mean CO ~=~ age + strain + \varepsilon$$

```{r age.effect.model.setupdata, echo=FALSE}
#run a age effect linear regression!
male.data <- AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$sex.y == "male",]

#remove all nas

#unorder the factors
class(male.data$strain.x) <- "factor"
class(male.data$subsp.x) <- "factor"

male.data.dom <- male.data[male.data$subsp.y == "Dom",]
male.data.dom <- male.data.dom[!(is.na(male.data.dom$Nmice) | male.data.dom$Nmice==""), ]

#MOLF is a low strain
male.data.musc.low <- male.data[(male.data$strain.x == "KAZ" | male.data$strain.x == "TOM" | male.data$strain.x == "AST" | male.data$strain.x == "MOLF"),]
male.data.musc.low <- male.data.musc.low[!(is.na(male.data.musc.low$Nmice) | male.data.musc.low$Nmice==""), ]

male.data.musc.high <- male.data[(male.data$strain.x == "PWD" | male.data$strain.x == "MSM" | male.data$strain.x == "SKIVE"),]
male.data.musc.high <- male.data.musc.high[!(is.na(male.data.musc.high$Nmice) | male.data.musc.high$Nmice==""), ]

male.data.outgroup <- male.data[(male.data$subsp.y == "Spretus" | male.data$subsp.y == "Spic" | male.data$subsp.y == "Caroli"),]
male.data.outgroup <- male.data.outgroup[!(is.na(male.data.outgroup$Nmice) | male.data.outgroup$Nmice==""), ]

```{r age.models, echo=FALSE}

@@

#summary(lm.me.OG)
as.data.frame( round(  summary(lm.me.dom)$coefficients, 6 ) )

as.data.frame( round(  summary(lm.me.musc.low)$coefficients, 6 ) )

as.data.frame( round(  summary(lm.me.musc.high)$coefficients, 6 ) )
```

Dom, no significant effects for age.

Musc low, no significant effect for strain or age.

Musc high, MSM and SKIVE have significant age effects on mean CO count

SKIVE has the greatest spread in ages for single mice (7,16,41 weeks)
There are more SKIVE males which I haven't quantified (at least 3, which are in a good age range)

@@

#AP_mouse_table_w.Ages <- add_category(AP_mouse_table_w.Ages)
#remove NAs
#AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[!(is.na(AP_mouse_table_w.Ages$Nmice) | #AP_mouse_table_w.Ages$Nmice==""), ]

@@

```{r dissection.effect.data.setup, echo=FALSE}

#AP_mouse_table_w.Ages$euth.date
